Figures

### 2016-01-02 scripts/figures.Rmd
read position figs

>>>>

cut.read.df<-subset(cut.df,Read_pos>32 & Read_pos<94)

h.cut.read.df<-hiseq.roc(cut.read.df,possible_tp,possible_vars)

ggplot(subset(h.cut.read.df,gc==4),aes(x=1-adj.specificity,y=adj.sensitivity))+geom_step(aes(color=exp.freq),size=2)+scale_color_brewer(palette = "Set1")+xlab("1-Specificity")+ylab("Sensitivity")+guides(color=guide_legend(title="Frequency"))+scale_y_continuous(limits=c(0,1))

h.cut.read.table<-hiseq.roc.table(cut.read.df,0.001,possible_tp,possible_vars)

knitr::kable(subset(h.cut.read.table,gc==5))
